---
title: "Developing Data Products - Assignment Week 3"
author: "Andre Dannemann"
date: "14 April 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

## Week 3 Assignment - Costs of Panini Sticker Collection

- <span style="font-size: 20px;">This is an R Markdown presentation on the cost of the Panini Sticker Collection for the World Soccer Championship 2018 in Russia.</span> 
- <span style="font-size: 20px;">I don't know, if collecting stickers for a certain sports event is as popular in the US. In Europe, it is.</span>  
- <span style="font-size: 20px;">For the world soccer championship 2018, Panini has a collection of 682 stickers. Each sticker costs 0.18 € (there are better offers, however, my calculations use the price of the single package with 5 stickers available at every store).</span>
- <span style="font-size: 20px;">My code simulates 100 collections without trading with other collectors, so purchasing all cards until the book is complete.</span> 

## Plotly plot
  
```{r libraries}
library(ggplot2)
library(plotly)
```
```{r collect_only}
nr_of_collectors <- 1
nr_of_sims <- 10
book <- vector("numeric",length = 682)
for(i in seq_along(book)) { book[i] = 0 }
cost <- 0.00
nr_of_cards <- vector("integer",length = 682)
for(i in seq_along(nr_of_cards)) { nr_of_cards[i] = 0 }
cost_vec <- vector("numeric", length = 682)
for(i in seq_along(cost_vec)) { cost_vec[i] = 0.00 }
collect_book_stats <- data.frame(nr_of_cards = 0, cost = 0.00)
add_collect_book_stats <- data.frame(cbind(nr_of_cards, cost_vec))
names(add_collect_book_stats) <- c("nr_of_cards", "cost")
mean_book_stats <- data.frame(cbind(nr_of_cards, cost_vec), type_of_value = "simulation")
#mean_book_stats
```
```{r}
for(k in 1:nr_of_sims) {
    for(i in 1:100000) {
        card_nr <- runif(1, min = 1, max = 683)
        cost <- cost + 0.18    
        card_nr <- as.integer(card_nr)
        if((book[card_nr] < nr_of_collectors)) {
            book[card_nr] <- book[card_nr] + 1
            cards_found <- sum(book) / nr_of_collectors
            if((cards_found %% 1 ) == 0) {
                add_collect_book_stats$nr_of_cards[cards_found] <- cards_found
                add_collect_book_stats$cost[cards_found] <- cost / nr_of_collectors
#                collect_book_stats <- rbind(collect_book_stats, add_collect_book_stats)            
            }
        }
        if((sum(book) / nr_of_collectors) >= 682) {
            collect_book_stats <- rbind(collect_book_stats, add_collect_book_stats)
            break
        }
    }
    for(m in 1:length(book)) { book[m] = 0 }
#    for(m in 1:length(doubles)) { doubles[m] = 0 }
#    for(m in 1:length(cost_vec)) { cost_vec[m] = 0 }
    cost <- 0.00
}
```
```{r}
#head(collect_book_stats)
#tail(collect_book_stats)
#dim(collect_book_stats)
#total_collect_stats
#dim(collect_book_stats)
#qplot(total_collect_stats$cost, binwidth = 10)
#qplot(book, cost, data = collect_book_stats)
```
```{r my_values}
rl_book_stats <- data.frame(nr_of_cards = c(54, 72, 91, 152),
                            cost_vec = c(9.9, 13.5, 17.1, 31.5),
                            type_of_value="real life")
#rl_book_stats
```
```{r calc_mean}
for(i in seq_along(mean_book_stats$nr_of_cards)) {
    mean_book_stats$nr_of_cards[i] <- i
    mean_book_stats$cost_vec[i] <- mean(collect_book_stats$cost[collect_book_stats$nr_of_cards == i])
#    mean_book_stats$type_of_value[i] <- "simulation"
}
#head(mean_book_stats)
#tail(mean_book_stats)
#g <- ggplot(mean_book_stats, aes(nr_of_cards, cost_vec))
#g <- g + geom_point()
#g <- g + geom_point(data = rl_book_stats, color = "red")
#g
all_book_stats <- rbind(mean_book_stats, rl_book_stats)
names(all_book_stats) <- c("nr_of_cards","costs","type_of_value")
plot_ly(all_book_stats, x=~nr_of_cards, y=~costs, color=~factor(type_of_value))
```
  
<span style="font-size: 20px;">The plot shows the simulations and my own experiences together. The "real life" points (four grey points) show my collection steps (up to now, 152 cards collected successfully).</span>